\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-04-24 doc/paper.tex
removed red comment in abstract.

  \begin{abstract}
   We introduce \fs, a MATHEMATICA package which generates a C++
   spectrum generator for any SUSY model, created with modularity and
   speed in mind.  \fs makes use of the existing \sarah package
   to obtain self energies, tadpole corrections and renormalisation
   group equations in any model.  \fs then generates C++ code for
   calculating spectra with a structure that is designed to be
   flexible. The user specifies the model supplying the
   superpotential, gauge structure and particle content in a \sarah
   model file. The user should also specify the boundary conditions in
   a separate \fs model file. {\color{red}( Do we want to keep this
     separate and in different places, add a script to put a \sarah
     model file in the right place or combine them?)}  Flexible SUSY
   then translates these into C++ code along with numerical routines
   for solving the renormalisation group equations, one loop
   electroweak symmetry breaking conditions and a solver routine for
   simultaneously solving for the spectrum.  The modular structure of
   the generated code allows for any individual component to be
   replaced with an alternative if available.  Indeed \fs has been
   intentionally designed to grow as alternative solvers and
   calculators are added.
  \end{abstract}
\begin{keyword}
sparticle, 
supersymmetry, 
Higgs
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}

>>>>

  \begin{abstract}
   We introduce \fs, a MATHEMATICA package which generates a C++
   spectrum generator for any SUSY model, created with modularity and
   speed in mind.  \fs makes use of the existing \sarah package
   to obtain self energies, tadpole corrections and renormalisation
   group equations in any model.  \fs then generates C++ code for
   calculating spectra with a structure that is designed to be
   flexible. The user specifies the model supplying the
   superpotential, gauge structure and particle content in a \sarah
   model file. The user should also specify the boundary conditions in
   a separate \fs model file.  Flexible SUSY
   then translates these into C++ code along with numerical routines
   for solving the renormalisation group equations, one loop
   electroweak symmetry breaking conditions and a solver routine for
   simultaneously solving for the spectrum.  The modular structure of
   the generated code allows for any individual component to be
   replaced with an alternative if available.  Indeed \fs has been
   intentionally designed to grow as alternative solvers and
   calculators are added.
  \end{abstract}
\begin{keyword}
sparticle, 
supersymmetry, 
Higgs
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}
